

# Question 1

## Creating Template

```{r}

Texevier::create_template_html(directory = "/Users/samanthascott/Desktop/20945043/Question1",
                          template_name = "Question1_html",
                          build_project = T, open_project = F)

```

## Code

```{r}
gc() 

library(pacman)
p_load(tidyverse, lubridate)

list.files('Question1/Code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

## Loading Data

```{r}
 library(readr)
 Deaths_by_cause <- read_csv("Question1/Data/Covid/Deaths_by_cause.csv")

```

```{r}
library(readr)
owid_covid_data <- read_csv("Question1/Data/Covid/owid-covid-data.csv")

```

## Graph 1

```{r}
g <- line_graph_continents(owid_covid_data)

```

As seen in the graph, the continents with the highest number of total cases is Europe and North America. African countries are seen to have not been as greatly by COVID than North American, South American and European countries. In comparison, the number of total countries in Africa seem almost insignificant in comparison to countries in other continents.

However, to accurately interpret this graph, it is imperative that one take in to consideration the population of the continents.

## Graph 2

```{r}
g <- brics_SI_deaths(owid_covid_data)

```

# Question 2

## Creating Template

```{r}

Texevier::create_template_html(directory = "/Users/samanthascott/Desktop/20945043/Question2",
                          template_name = "Question2_html",
                          build_project = T, open_project = F)

```

## Code

```{r}
gc() 

library(pacman)
p_load(tidyverse, lubridate)

list.files('Question2/Code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

## Loading Data

```{r}
library(readr)
london_weather <- read_csv("Question2/Data/London/london_weather.csv")

```

```{r}
library(readr)
SUN_Hours <- read_csv("~/Desktop/20945043/Question2/Data/SUN Hours.csv")
```

## Graphs 

```{r}
g <- london_code(london_weather, SUN_Hours)
```

# Question 3

## Creating Template

```{r}

Texevier::create_template_html(directory = "/Users/samanthascott/Desktop/20945043/Question3",
                          template_name = "Question3_html",
                          build_project = T, open_project = F)

```

## Code

```{r}
gc() 

library(pacman)
p_load(tidyverse, lubridate)

list.files('Question3/Code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

## Loading Data

# Question 4

## Creating Template

```{r}

Texevier::create_template_html(directory = "/Users/samanthascott/Desktop/20945043/Question4",
                          template_name = "Question4_html",
                          build_project = T, open_project = F)

```

## Code

```{r}
gc() 

library(pacman)
p_load(tidyverse, lubridate)

list.files('Question4/Code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

## Loading Data

```{r}
library(readr)
credits <- read_csv("~/Desktop/20945043/Question4/Data/netflix/credits.csv")
```

```{r}
library(readr)
titles <- read_csv("~/Desktop/20945043/Question4/Data/netflix/titles.csv")
```

## Graphs and Statistics

```{r}
g <- netflix_code(titles)
```

## Figure 4.1

|            | Movies   | Shows    |
|------------|----------|----------|
| IMDb score | 6.266980 | 7.017377 |

: IMDb Score: Movies vs Shows

According to the data, shows did better than movies. 

According to the accompanying data, the combination ['scifi', 'family', 'fantasy', 'animation', 'action'] genre is most 
